### 2020-01-30 defesa/tex/chapter/mcd.tex
wip

In this chapter, we introduce a version of the classical Euclidean norm PMCLP where each facility has a given coverage radius. 
We refer to this problem as \sigla{MCD}{Maximum Covering by Disks}. We also propose a method for it intending to adapt it for the elliptical PMCLP that will be introduced in the next chapter.

@@

A solution for an instance of MCD is determined by $Q:=(q_1, \dots, q_m) \in \R^{2m}$ which specifies the center of every disk in $\D$.
The coverage region of the $j$-th disk centered at $q_j$ is denoted by $D_j(q_j)$. Finally, let $w : 2^{\Pp} \mapsto \R_{\ge0}$ be the function

\begin{equation}\label{eq:subset_w}
w(A) = \sum_{j : p_j \in A} w_j,
\end{equation}
which takes a subset of $\Pp$ and returns the sum of the weights of every point in it; then an optimal solution of MCD is given by the optmization problem:

@@

As a remark, it is important to note that MCD is a slightly different PMCLP than the one introduced in the first study on the subject in \citeonline{church:1984}. There, a coverage radius is given for each demand, rather than for each facility, and a demand is only considered covered if a facility is located within its radius.

@@

The method proposed in \citeonline{church:1984} involves the creation of a \sigla{CLS}{Candidate List Set}, which is a finite set of possible solutions, for each facility. After a CLS is constructed, a complete search is executed to find the best solution. That is why, as an heuristic, it is a good idea to create small CLSs that somehow can still provide good solutions.

As this work is developed towards the creation of an exact method for MCD, the focus is on constructing a CLS that contains an optimal solution.
This is done in \citeonline{church:1984} where a circle is defined for every demand point, and a \sigla{CIPS}{circle intersection point set} is constructed containing the demand points and every pairwise circle intersection.
Here, we introduce a similar approach based on works found on the case for only one disk and describe a $\bigO(n^2\lg{n})$ algorithm for it.

@@

\section{Maximum Weight Clique Problem}

An instance of MWC is given by a set of points $\Pp:=\{p_1,\dots,p_n\}$, with $p_i \in \R^2$; a set of unit disks $\D:=\{D_1(p_1),\dots,D_n(p_n)\}$; and a set of weights $\Ww=\{w_1, \dots, w_n\}$ with the $i$-th disk having a weight $w_i\in \R_{>0}$ assigned to it. To make the notation less cluttered, we use, in this problem, $D_j:=D_j(p_j)$, for $j\in\{1, \dots, n\}$.

A clique, in this context, is a non-empty intersection region of one or more disks, and its weight is the sum of the weights of those disks in the intersection.
Following this, a solution for MWC can be defined as just a point $q\in\cup_{j=1}^n D_j$ which is inside any of the given disks in $\D$.
From a solution $q$, the corresponding clique $S$ can be obtained by intersecting every disk that contains $q$:

\begin{equation*}
S = \bigcap_{j : q \in D_j} D_j.
\end{equation*}
With a geometric observation, though, the number of possible values for the solution can be reduced.
Let $\partial \D = \{ \partial D_1, \dots, \partial D_n \}$ be the set of circles corresponding to each disk in $\D$, it is possible to see that any clique has at least one point on its border that is in the intersection of two circles in $\partial D$ or, in the case where the clique is composed of only one disk, it contains the center of its only disk. Because of that, $q$ can be actually limited to the set of pairwise intersections of $\partial \D$ as well as the set of centers of each disk $\Pp$. Then, with this observation, an optimal solution of MWC can be defined by the optimization problem

\begin{equation*}
\max_{q} \sum_{D_k \cap q \neq \emptyset} w_k,
\end{equation*}
with $q \in \{\partial D_i \cap \partial D_j : 1 \le i < j \le n\} \cup \Pp$. With this new specification of the solution's search space, it can be shown that given an instance of MWC, an optimal solution for it can be found by going through $\binom{n}{2} + n = \bigO(n^2)$ possible ones.

@@

\begin{figure}[H]
\centering

    \caption{Three disks that have non-empty pairwise intersection among them, but no common intersection.}
    %\begin{tikzpicture}[scale=1]
    %\draw [help lines] (-5,-3) grid (5,3);
    %\draw (0,0) circle (1cm) (0.9,1.6) circle (1cm) (-0.9,1.6) circle (1cm);

    %a^2-b^2=c^2 -> c^2=25-9=16 -> c=4

    %\draw[fill] (0.9,1.6) circle [radius=.5pt];
	%\draw[fill] (0,0) circle [radius=.5pt];
    %\draw[fill] (-0.9,1.6) circle [radius=.5pt];

    %\node[below] at (0,0) {$p_1$};
    %\node[below] at (0.9, 1.6) {$p_2$};
    %\node[below] at (-0.9, 1.6) {$p_3$};

    %\draw [-] (-5,0) -- (5,0);
     %\draw [-] (0,-3) -- (0,3);
     %\draw [|-|] (0.001,-0.1) -- (4.999,-0.1);
    %\end{tikzpicture}

    \includegraphics[scale=.35]{tex/figures/three_disks_no_intersection.pdf}
    \label{fig:three_disks_no_intersection}
    \fautor
\end{figure}

@@

Given an instance of MCD1, the equivalent MWC intance is obtained by defining the set $\D$ to contain the disks centered at $\Pp$ and setting the weight of every disk to be the weight of its corresponding point in $\Pp$. A disk $D_i$ will represent the area where a disk can be placed in order to cover $p_i$. This means that a intersection between some disks is a region where a disk could be placed to cover the corresponding points.

@@

@@

The algorithm described here is based on the one in \citeonline{drezner}, also with some ideas from \citeonline{inplace:2014} and \citeonline{cabello:2006}. It has a run time complexity of $\bigO(n^2\log{n})$ and uses $\bigO(n)$ of extra space. It is worth noting, however, that a $\bigO((n+K)\log{n})$ run time, with $K$ being the number of intersections, can be obtained by using the algorithm in \citeonline{bentley:1979} to find all the intersections among the $n$ circumferences.

@@

\begin{definicao}\label{def:inter_arc}
    Let $D_i$ and $D_j$ be two unit disks with non-empty intersection, and $(\theta_1, \theta_2) \in [0,2\pi)^2$ be the two angles that $\partial D_i$ and $\partial D_j$ intersect, with the condition that $(\theta_1,\theta_2)$ defines an arc (counter-clockwise order) of $D_i$ that is the border of $D_i \cap D_j$. Then, define $\Gamma_+(i,j) = \theta_1$ and $\Gamma_-(i,j) = \theta_2$. For convenience, if $D_i$ is tangent to $D_j$, then $\theta_1=\theta_2$; and if $i=j$, then $\Gamma_+(i, j)=0$ and $\Gamma_-(i,j)=2\pi$.
\end{definicao}

@@

    \caption{Three disks and their intersection points.}
    \includegraphics[scale=.36]{tex/figures/3_disks_intersect.pdf}
%    \input{tex/img2.tex}
    \fautor
    \label{fig:3disks_intersect}
\end{figure}

@@

With \autoref{def:inter_arc} in hand, we can establish the basis of the algorithm for MWC. For every disk $D_i$, let us describe an algorithm that gets the best clique which $D_i$ is part of. This way, an algorithm for MWC just uses that method for every disk and returns the best solution found. Firstly, let $A_i$ be a circular list that contains the intersection angles of $\partial D_i$ with every circle in $\partial \D$ defined as

\begin{equation*}
A_i = \bigcup_{j=1}^n \{ \Gamma_-(i,j), \Gamma_+(i,j) \}.
\end{equation*}
Assume also that $A_i$ is sorted in ascending order by the angle values with ties being broken by prioritizing opening angles.

@@

\begin{equation}\label{eq:b_i}
B_i = A_i\cup\bigcup_{j=1}^n \{ 2\pi+\Gamma_-(i,j), 2\pi+\Gamma_+(i,j) \}.
\end{equation}
Assuming $B_i$ is sorted with the same criteria as $A_i$. A simple traversal, starting at the first element and going until the last one, simulates a traversal on the circular list $A_i$.
This works because for any pair of disks $D_i$, $D_j$; $B_i$ contains $\Gamma_+(i,j) < \Gamma_-(i,j) + 2\pi$. That is, the algorithm encounters an opening angle before reaching a closing one for any circle.

In \autoref{fig:array_disks}, the intersection points between $\partial D_1$ (solid border) with $\partial D_2, \partial D_3$, and $\partial D_4$ (dashed border) are shown with a plus or minus sign indicating opening or closing intersection angles. 
The intersection list $B_1$ is also displayed in \autoref{fig:array_disks} along with the size of the set of active disks $Q$ after processing a point in $B_1$ -- this is exactly what \autoref{algoritmo:mcd_1} for MWC does for every disk. 
It is possible to see that the optimal clique highlighted in \autoref{fig:array_disks} is enclosed by the arcs defined by $\Gamma_+(1,4)$ and $\Gamma_-(1,4)$, and can also be identified by following $B_1$ while keeping track of $Q$.
The special intersection point of $\partial D_1$ with itself can also be seen in \autoref{fig:array_disks}. Its usage is very convenient as with $\Gamma_+(1, 1)$ and $\Gamma_-(1,1)$  in $B_1$, the algorithm inserts $D_1$ in the set of active disks before processing any point, and removes $D_1$ only after every point has been processed.

Finally, we define \autoref{algoritmo:mcd_1} for MWC. Given an instance $(\Pp, \Ww)$ of MWC, the algorithm uses the approach described here of keeping a set of active disks while traversing the list $B_i$. It returns a point that is inside an optimal clique, this way \autoref{algoritmo:mcd_1} can also be used to get an optimal solution for an instance $(\Pp, \Ww)$ of MCD1.

@@

@@

\begin{algoritmo}[b]
\caption{Algorithm for MWC.}\label{algoritmo:mcd_1}
\begin{algorithmic}[1]
\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and a set of weights $\Ww=\{w_1, \dots, w_n\}$.}
\Ensure{A point that is inside the maximum weight clique of unit disks.}

\Procedure{$MWC$}{$\Pp, \D, \Ww$}
\State Let $\D=\{D_1(p_1), \dots, D_n(p_n)\}$ be a set of unit disks
\State $Q_{best} \gets \{\}$
\State $q^* \gets$ $p_1$
\ForAll{$D_i \in \Pp$}
\State Let $B_i$ be the list of intersection angles of $D_i(p_i)$ as defined by \autoref{eq:b_i}

\State $Q \gets \{\}$ \Comment{The set of active disks.}
\For{$\theta \in B_i$}\Comment{Assuming $B_i$ is sorted.}
\State Let $D_j$ be the disk, such that $\theta \in D_j(p_j)\cap D_i(p_i)$
\If{$\theta$ is a opening angle}
\State $Q \gets Q \cup \{D_j\}$
\Else
\State $Q \gets Q \setminus \{D_j\}$
\EndIf
\If{$w(Q_{best}) < w(Q)$} 
\State $Q_{best} \gets Q$
\State $q^* \gets$ point corresponding to the intersection angle $\theta$
\EndIf

>>>>

In this chapter, we introduce a version of the classical Euclidean norm PMCLP, where each facility has a given coverage radius. 
We refer to this problem as \sigla{MCD}{Maximum Covering by Disks}. We also propose an algorithm for it to later adapt it for the elliptical PMCLP in the next chapter.

@@

A solution for an instance of MCD is determined by $Q:=(q_1, \dots, q_m) \in \R^{2m}$, which specifies the center of every disk in $\D$. Let $w: 2^{\Pp} \mapsto \R_{\ge0}$ be a function, which takes a subset of $\Pp$ and returns the sum of the weights of every point in it, defined as

\begin{equation}\label{eq:subset_w}
w(A) = \sum_{j : p_j \in A} w_j.
\end{equation}
Then an optimal solution of MCD is formulated as a solution of

@@

It is worth mentioning that MCD is a slightly different PMCLP than the one introduced in the first study on the subject in \citeonline{church:1984}. There, a coverage radius is given for each demand, rather than for each facility, and a demand point is considered covered if a facility is located within its radius.

@@

The method proposed in \citeonline{church:1984} involves the construction of a finite set of locations where each facility can be placed as a way of transforming a problem, where every point in $\R^2$ is a possible solution, into one where only a finite number of possibilities need to be considered. This set of possible locations is called \sigla{CLS}{Candidate List Set}.

In \citeonline{church:1984}, a CLS is set to be the \sigla{CIPS}{circle intersection point set}, which contains the intersection of circles with fixed radii centered at every demand point. This approach provides an optimal solution if a complete search on the CLS for every facility is done.

We introduce, in this chapter, a $\bigO(n^2\lg{n})$ algorithm that returns a CLS for each facility, which is based on the idea presented in \citeonline{church:1984} and in the works for the one disk case by \citeonline{chazelle:1986} and \citeonline{cabello:2006}. We refer to the CLS for the $j$-th facility as $S_j$ and prove that, indeed, an optimal solution can be found by just considering the centers in $S_j$ for each facility.

@@

\section{Maximum Weight Clique}

An instance of the \sigla{MWC}{Maximum Weight Clique} is given by a list of points \mbox{$\Pp:=\{p_1,\dots,p_n\}$}, with $p_i \in \R^2$ representing the center of a unit disk;  and \mbox{$\Ww:=\{w_1, \dots, w_n\}$}, with $w_i\in \R_{>0}$ being the weight of the $i$-th unit disk. We also define a list $\D=\{D_1, \dots, D_n\}$, such that $D_i$, $i\in\{1,\dots,n\}$, is a unit disk centered at $p_i$ having weight $w_i$ assigned to it.

A clique, in this context, is a non-empty intersection region of one or more disks, and its weight is the sum of the weights of those disks in the intersection.
Following this, a solution for MWC can be defined as just a point $q\in\cup_{j=1}^n D_j$, which is inside any of the given disks in $\D$.
From a solution $q$, the corresponding clique $S$ can be obtained by intersecting every disk that contains $q$ as follows

\begin{equation*}
S = \bigcap_{j : q \in D_j} D_j.
\end{equation*}

With a geometric observation, though, the number of possible values for the solution can be reduced.
Let $\partial \D = \{ \partial D_1, \dots, \partial D_n \}$ be the set of circles corresponding to each disk in $\D$. 
Unless a clique is formed by only one disk, its boundary contains at least two points, which are the intersection of two circles that are part of the clique.
Because of that, $q$ can be limited to the set of pairwise intersections of $\partial \D$ as well as the set of centers of each disk $\Pp$, which considers the case where the optimal clique is composed of only one disk. With this observation, an optimal solution of MWC can be defined by the optimization problem

\begin{equation*}
\max_{q} \sum_{D_k \cap q \neq \emptyset} w_k,
\end{equation*}
with $q \in \{\partial D_i \cap \partial D_j : 1 \le i < j \le n\} \cup \Pp$. With this new specification of the solution's search space, given an instance of MWC, an optimal solution can be found by going through $\binom{n}{2} + n$ points, that is, $\bigO(n^2)$ points.

@@

@@

Given an instance of MCD1, the equivalent MWC intance is obtained by defining the set $\D$ to contain the disks centered at $\Pp$ and setting the weight of every disk to be the weight of its corresponding point in $\Pp$. A disk $D_i$ will represent the area where a disk can be placed in order to cover $p_i$. This means that an intersection between some disks is a region where a disk could be placed to cover the corresponding points.

@@

\begin{figure}[h]
	\centering

	\caption{Three disks that have non-empty pairwise intersection among them, but no common intersection.}

	\includegraphics[scale=.25]{tex/figures/three_disks_no_intersection.pdf}
	\label{fig:three_disks_no_intersection}
	\fautor
\end{figure}

@@

The algorithm described here is based on the one in \citeonline{drezner}, also with some ideas from \citeonline{inplace:2014} and \citeonline{cabello:2006}. It has a run time complexity of $\bigO(n^2\log{n})$ and uses $\bigO(n)$ of extra space. It is worth noting, though, that a $\bigO((n+K)\log{n})$ run time, with $K$ being the number of intersections, can be obtained by using the algorithm in \citeonline{bentley:1979} to find all the intersections among the $n$ circumferences.

@@

\begin{definicao}\label{def:inter_arc}
    Let $D_i$ and $D_j$ be two unit disks with non-empty intersection, and \mbox{$(\theta_1, \theta_2) \in [0,2\pi)^2$} be the two angles that $\partial D_i$ and $\partial D_j$ intersect, with the condition that $(\theta_1,\theta_2)$ defines an arc (counter-clockwise order) of $D_i$ that is the border of $D_i \cap D_j$. Then, define $\Gamma_+(i,j) = \theta_1$ and $\Gamma_-(i,j) = \theta_2$. For convenience, if $D_i$ is tangent to $D_j$, then $\theta_1=\theta_2$; and if $i=j$, then $\Gamma_+(i, j)=0$ and $\Gamma_-(i,j)=2\pi$.
\end{definicao}

@@

    \caption{Three disks and their intersection points.}
    \includegraphics[scale=.3]{tex/figures/3_disks_intersect.pdf}
%    \input{tex/img2.tex}
    \fautor
    \label{fig:3disks_intersect}
\end{figure}

@@

With \autoref{def:inter_arc} in hand, we can establish the basis of the algorithm for MWC. For every disk $D_i$, let us describe an algorithm that gets the best clique which $D_i$ is part of. This way, an algorithm for MWC just uses that method for every disk and returns the best solution found. Firstly, let $A_i$ be a circular list that contains the intersection angles of $\partial D_i$ with every circle in $\partial \D$ defined as
\begin{equation*}
A_i = \bigcup_{j=1}^n \{ \Gamma_-(i,j), \Gamma_+(i,j) \}.
\end{equation*}
Assume also that $A_i$ is sorted in ascending order by the angle values with ties being broken by prioritizing opening angles.

@@

\begin{equation}\label{eq:b_i}
B_i = A_i\cup\bigcup_{j=1}^n \{ 2\pi+\Gamma_-(i,j), 2\pi+\Gamma_+(i,j) \}.
\end{equation}
Assuming $B_i$ is sorted with the same criteria as $A_i$, a simple traversal, starting at the first element and going until the last one, simulates a traversal on the circular list $A_i$.
This works because for any pair of disks $D_i$, $D_j$; $B_i$ contains $\Gamma_+(i,j) < \Gamma_-(i,j) + 2\pi$. That is, the algorithm encounters an opening angle before reaching a closing one for any circle.

In \autoref{fig:array_disks}, the intersection points between $\partial D_1$ (solid border) with $\partial D_2, \partial D_3$, and $\partial D_4$ (dashed border) are shown with a plus or minus sign indicating opening or closing intersection angles. 
The intersection list $B_1$ is also displayed in \autoref{fig:array_disks} along with the size of the set of active disks $Q$ after processing a point in $B_1$ -- this is exactly what \autoref{algoritmo:mcd_1} for MWC does for every disk. 
It is possible to see that the optimal clique highlighted in \autoref{fig:array_disks} is enclosed by the arcs defined by $\Gamma_+(1,4)$ and $\Gamma_-(1,4)$, and can also be identified by following $B_1$ while keeping track of $Q$.
The special intersection point of $\partial D_1$ with itself can also be seen in \autoref{fig:array_disks}. Its usage is very convenient as with $\Gamma_+(1, 1)$ and $\Gamma_-(1,1)$  in $B_1$, the algorithm inserts $D_1$ in the set of active disks before processing any point, and removes $D_1$ only after every point has been processed.
\begin{figure}[H]
	\centering

@@

Finally, we define \autoref{algoritmo:mcd_1} for MWC. Given an instance $(\Pp, \Ww)$ of MWC, the algorithm uses the approach described here of keeping a set of active disks while traversing the list $B_i$. It returns a point that is inside an optimal clique, this way \autoref{algoritmo:mcd_1} can also be used to get an optimal solution for an instance $(\Pp, \Ww)$ of MCD1.
\clearpage
\begin{algoritmo}[!htb]
	\caption{Algorithm for MWC.}\label{algoritmo:mcd_1}
	\begin{algorithmic}[1]
		\Require{A set of points $\Pp=\{p_1,\dots,p_n\}$, and a set of weights $\Ww=\{w_1, \dots, w_n\}$.}
		\Ensure{A point that is inside the maximum weight clique of unit disks.}

		\Procedure{$MWC$}{$\Pp, \Ww$}
		\State Let $\D=\{D_1, \dots, D_n\}$ be a set of unit disks, with centers in $\Pp$ and weights in $\Ww$

		\State $Q_{best} \gets \{\}$
		\State $q^* \gets$ $p_1$
		\ForAll{$D_i \in \D$}
		\State Let $B_i$ be the list of intersection angles of $D_i$ as defined by \autoref{eq:b_i}

		\State $Q \gets \{\}$ \Comment{The set of active disks.}
		\For{$\theta \in B_i$}\Comment{Assuming $B_i$ is sorted.}
		\State Let $D_j$ be the disk, such that $\theta \in D_j\cap D_i$
		\If{$\theta$ is a opening angle}
		\State $Q \gets Q \cup \{D_j\}$
		\Else
		\State $Q \gets Q \setminus \{D_j\}$
		\EndIf
		\If{$w(Q_{best}) < w(Q)$} 
		\State $Q_{best} \gets Q$
		\State $q^* \gets$ point corresponding to the intersection angle $\theta$
		\EndIf

@@

### 2020-01-30 defesa/tex/chapter/mce.tex
wip

Axis-parallel ellipses are defined as the set of points that satisfy \autoref{equation:pellipse}. Note that all it takes to describe an axis-parallel ellipse is a pair of positive real numbers $(a,b) \in \R_{>0}^2$, also called its shape parameters, and a center point $q \in \R^2$.

@@

Then, a solution for MCE is given by $Q:=(q_1, \dots, q_m)\in\R^{2m}$, with $q_j$ being the center of $j$-th ellipse. Finally, let $w : 2^\Pp \mapsto \R_{\ge0}$ as defined by \autoref{eq:subset_w}, then an optimal solution of MCE is given by the optimization problem

@@

In the next sections, we first describe a method for the case with only one ellipse, and then use it in the algorithm for multiple ellipses to construct a CLS containing an optimal solution.

@@

The case with only one ellipse is considered first because it will be adapted to become the basis of the algorithm for more than one ellipse. We refer to this version as \sigla{MCE-1}{Maximum Cover by One Ellipse}.

An instance of MCE-1 has $m=1$, and we set $(a, b):=(a_1, b_1)$, and $\E := \{E\}$. Therefore, an instance of MCE-1 is described by the tuple $(\Pp; \Ww; (a, b))$. A solution of MCE-1 is then given by a point $q\in\R^2$, and an optimal solution is given by the optimization problem

@@

\begin{equation*}
\phi_{1,2}(p_i) = \begin{cases}
\Gamma_+(1,2) & angle(\gamma_1'(t_i^{(1)}), -\gamma_2(t_i^{(2)})) > \pi\\
\Gamma_-(1,2) & angle(\gamma_1'(t_i^{(1)}), -\gamma_2(t_i^{(2)})) < \pi.
\end{cases}
\end{equation*}
At last, the case where that angle is equal to $\pi$ happens only when both ellipses intersect at only one point. This case has to be treated separately as, by \autoref{def:inter_arc}, we need to have two equal intersection points: one as $\Gamma_+(1,2)$ and the other as $\Gamma_-(1,2)$.

@@

        \item[]
        \Procedure{$MCE$}{$\Pp, \Ww, \Rr$}
	    \State \Return $MCE_{bt}(\Pp, \Ww, \Rr, 1)$
        \EndProcedure

        \Procedure{$MCE_{bt}$}{$Z, \Ww, \Rr, j=1$}
        \If{$j = m+1$}
        \State \Return $0$
        \EndIf

@@

        \If{$w(\cup_{k=j}^m Z \cap E_k(q_k)) >  w(\cup_{k=j}^m Z \cap E_k(q_k^*))$}
        \State $(q_j^*, \dots, q_j^*) \gets(q_j, \dots, q_m)$
        \EndIf
        \EndFor

@@

	\ForAll{$I=\{i_1, \dots, i_k\} \subset \{1, \dots, m\}$, such that $|I|=k$}

		\State $(q_1, \dots, q_k) \gets MCE(\Pp, \Ww, \{(a_j, b_j) \in \Rr: j \in I\})$

>>>>

Axis-parallel ellipses are defined as the set of points that satisfy \autoref{equation:pellipse}. All it takes to describe one is a pair of positive real numbers $(a,b) \in \R_{>0}^2$, with $a>b$, also called its shape parameters, and a center $q \in \R^2$.

@@

A solution for MCE is given by $Q:=(q_1, \dots, q_m)\in\R^{2m}$, with $q_j$ being the center of $j$-th ellipse. Let $w : 2^\Pp \mapsto \R_{\ge0}$ as defined by \autoref{eq:subset_w}, then an optimal solution of MCE is given by the optimization problem

@@

In the next sections, we first study the specific case of MCE with only one facility and discuss that the results of \autoref{chapter:pmclp} still apply when ellipses are used instead of disks. After that, we use the approach mentioned in \autoref{chapter:pmclp} of constructing a CLS for each facility and propose an algorithm for MCE.

@@

The case with only one ellipse is considered first because it will be adapted to become the basis of the algorithm for more than one ellipse. We refer to this version as \sigla{MCE1}{Maximum Cover by One Ellipse}.

An instance of MCE1 has $m=1$, and we set $(a, b):=(a_1, b_1)$, and $\E := \{E\}$. Therefore, an instance of MCE1 is described by the tuple $(\Pp; \Ww; (a, b))$. A solution of MCE1 is then given by a point $q\in\R^2$, and an optimal solution is given by the optimization problem

@@

\begin{equation*}
\phi_{1,2}(p_i) = \begin{cases}
\Gamma_+(1,2) & angle(\gamma_1'(t_i^{(1)}), -\gamma_2(t_i^{(2)})) > \pi\\
\Gamma_-(1,2) & angle(\gamma_1'(t_i^{(1)}), -\gamma_2(t_i^{(2)})) < \pi.
\end{cases}
\end{equation*}
Lastly, the case where that angle is equal to $\pi$ happens only when both ellipses intersect at only one point. This case has to be treated separately as, by \autoref{def:inter_arc}, we need to have two equal intersection points: one as $\Gamma_+(1,2)$ and the other as $\Gamma_-(1,2)$.

@@

        \item[]
        \Procedure{$MCE$}{$\Pp, \Ww, \Rr$}
	    \State \Return $MCE_{bt}(\Pp, \Ww, \Rr, 1)$
        \EndProcedure
        \State
        \Procedure{$MCE_{bt}$}{$Z, \Ww, \Rr, j$}
        \If{$j = m+1$}
        \State \Return $0$
        \EndIf

@@

        \If{$w(\cup_{k=j}^m Z \cap E_k(q_k)) >  w(\cup_{k=j}^m Z \cap E_k(q_k^*))$}
        \State $(q_j^*, \dots, q_m^*) \gets(q_j, \dots, q_m)$
        \EndIf
        \EndFor

@@

	\ForAll{$I=\{i_1, \dots, i_k\} \subset \{1, \dots, m\}$}

		\State $\Rr' \gets \{(a_j, b_j) \in \Rr: j \in I\}$
		\State $(q_1, \dots, q_k) \gets MCE(\Pp, \Ww, \Rr')$

### 2020-01-30 defesa/tex/chapter/mcer.tex
wip

This section introduces the elliptical PMCLP where there is no axis-parallel constraint, and the ellipses can be freely rotated. We refer to this problem as \sigla{MCER}{Maximal Covering by Ellipses with Rotation}. In comparison with MCE, this problem introduces a new variable that is responsible for determining the rotation angle of every ellipse, making MCER a more challenging problem.

@@

The second and third cases are addressed by \autoref{lema:3pnts}. 
Consider the second case to be the one where the $j$-ellipse covers more than one point and there is no equivalent solution with three points on the its border. 
By \autoref{lema:3pnts}, $(Q^*, \Theta^*)$ can be represented by a solution that has some pair of points $u, v$ on the ellipse's border, and is rotated by some angle in $\Phi_j(u,v)$. 
As only one angle is needed, we define $\theta_{uv}$ as the angle that makes the major-axis of the ellipse to be aligned with the line that passes through $u$ and $v$; this angle surely is in $\Phi_j(u,v)$ as the longest segment that crosses an ellipse is its major-axis.
Having said that, we refer to $S_j^{(2)}$ the set of possible solutions that takes this case into account; we define it as
\begin{equation}
S_j^{(2)} = \bigcup_{\{u, v\} \subset \Pp} \{(q, \theta_{uv})\in \R^2\times\R: \{u,v\} \subset \partial E_j(q, \theta_{uv})\}.\\
\end{equation}
For a pair of points $u, v$, determining every ellipse with a fixed rotation angle that has $u$ and $v$ on its border is equivalent to determining the intersection points of two axis-parallel ellipses with the same shape parameters. This problem is discussed with great detail in \autoref{chapter:ellipses_intersection}.

>>>>

This chapter introduces the elliptical PMCLP where there is no axis-parallel constraint, and the ellipses can be freely rotated. We refer to this problem as \sigla{MCER}{Maximal Covering by Ellipses with Rotation}. In comparison with MCE, this problem introduces a new variable that is responsible for determining the rotation angle of every ellipse, making MCER a more challenging problem.

@@

The second and third cases are addressed by \autoref{lema:3pnts}. 
Consider the second case to be the one where the $j$-ellipse covers more than one point and there is no equivalent solution with three points on the its border. 
By \autoref{lema:3pnts}, $(Q^*, \Theta^*)$ can be represented by a solution that has some pair of points $u, v$ on the ellipse's border, and is rotated by some angle in $\Phi_j(u,v)$. 
As only one angle is needed, we define $\theta_{uv}$ as the angle that makes the major-axis of the ellipse to be aligned with the line that passes through $u$ and $v$; this angle surely is in $\Phi_j(u,v)$ as the longest segment that crosses an ellipse is its major-axis.
Having said that, we refer to $S_j^{(2)}$ the set of possible solutions that takes this case into account; we define it as
\begin{equation}
S_j^{(2)} = \bigcup_{\{u, v\} \subset \Pp} \{(q, \theta_{uv})\in \R^2\times\R: \{u,v\} \subset \partial E_j(q, \theta_{uv})\}.\\
\end{equation}
For a pair of points $u, v$, determining every ellipse with a fixed rotation angle that has $u$ and $v$ on its border is equivalent to determining the intersection points of two axis-parallel ellipses with the same shape parameters. This problem is discussed with great detail in \autoref{section:ellipses_intersection}.
